\begin{enumerate}[label=\arabic*.] \setcounter{enumii}{11}
\justifying 
%\hspace{.25cm}

% 12
\item \underline{\textbf{K. Chung}}, \textit{et al.}, ``Demonstration of a bi-directionally tunable arrayed waveguide grating with ultra-low thermal power using S-shaped architecture and parallel-circuit configuration,'' \textit{Opt. Express}, \textbf{30}(14), 25842--25854 (2022).

% 13
\item J. Su, \underline{\textbf{K. Chung}}, \textit{et al.}, ``Ge p-i-n Photodiode as 60-Gbit/s Optical NRZ-OOK Data Receiver,'' \textit{IEEE J. Lightw. Technol.}, \textbf{40}(13), 4326--4336 (2022).

% 14
\item Y. Shih, \underline{\textbf{K. Chung}}, \textit{et al.}, ``Partial Parabolic Single Layer Crossing for Silicon-on-Insulator Nanophotonic Waveguides,'' \textit{IEEE Photon. J.}, \textbf{14}(2), 1--6 (2022).

% 15
\item D. Lin, \underline{\textbf{K. Chung}}, \textit{et al.}, ``Pre-Compensating the Shifted Power-to-Bias Response of Si Waveguide Modulator Induced by High-Speed Encoding,'' \textit{Conference on Lasers and Electro-Optics, Technical Digest Series (Optica Publishing Group, 2022)}, paper JTh3B.29.

% 16
\item Z. Ciou, \underline{\textbf{K. Chung}}, \textit{et al.}, ``Beyond 60-Gbit/s Modulation of Impedance Mismatched Silicon MZI Modulator,'' \textit{2021 IEEE 17th International Conference on Group IV Photonics (GFP)}, 1--2 (2021).

% 17
\item J. Su, \underline{\textbf{K. Chung}}, \textit{et al.}, ``Impulse Response and Noise Figure of a 50-Gbps O-band Ge p-i-n Waveguide Photodiode with High Responsivity,'' \textit{2021 30th Wireless and Optical Communications Conference (WOCC)}, 43--45 (2021).

% 18
\item S. Kao, \underline{\textbf{K. Chung}}, \textit{et al.}, ``High-Baud-Rate 32-QAM OFDM Single-arm and Dual-arm Encoded Silicon Mach-Zehnder Modulator,'' \textit{2021 30th Wireless and Optical Communications Conference (WOCC)}, 46--48 (2021).

\end{enumerate}
